---
title: "Antecedent temperature experiment"
output: 
  github_document:
  html_preview: True
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE
                      )
```

## sample summary

<details>
  <summary>click to open</summary>
Soils from northwest Alaska were homogenized and pre-incubated at -2 and -6 degrees Celsius for three months after which they were incubated at 2,4,6,8,10 degrees Celsius for one week. After the week long incubation soils were extracted using 0.5M K2SO4, and chloroform extracted to measure microbial biomass and nutrient concentrations. Sub-samples were also sent to PNNL for more comprehensive analysis of organic matter using FTICR, NMR, GC-MS and LC-MS techniques. Lipidomics were also performed to ascertain if there were any significant shifts lipids.

```{r analyte-completion, eval= TRUE}
tar_read(sample_key) %>% knitr::kable()
```

</details>

---

## Respiration results

<details>
  <summary>click to open</summary>
Respiration measurements were taken daily during the incubation using a Li-850 bench top respiration unit. Below are the respiration rates for each sample, as well as the calculates accumulative respiration rates.linear models are also drawn in represented color, with 95% confidence interval.    

```{r , fig.height=6, fig.width=9, results='hide'}
tar_read(gg_respiration)
```

</details>


---

## Soil Nutrients
<details>
  <summary>click to open</summary>
Soil K2SO4 extracts were utilized to measure ammonium, Nitrate, Total free primary amines, phosphate, Total reducing sugars. Below are the concentration data. An asterisks indicates a significant (p<= 0.05) difference in pre-incubation temperature. 

```{r , fig.height=6, fig.width=6, results='hide'}
tar_read(gg_nutrients)
```
</details>

---

## Microbial biomass
<details>
  <summary>click to open</summary>
Soil K2SO4 extracts were utilized to measure ammonium, Nitrate, Total free primary amines, phosphate, Total reducing sugars. Below is the concentration data.An asterisks indicates a significant (p<= 0.05) difference in pre-incubation temperature.

```{r , fig.height=3, fig.width=6, results='hide'}
tar_read(gg_MicrobialBiomass)
```
</details>

---

## Stats Table
<details>
  <summary>click to open</summary>
  
  Respiration rates were assessed using a Linear Mixed-Effects Models (lme function from package nlme). Incubation day, incubation temperature, and preincubation temperature were all shown to be significant. See table below for p-values. 
  Microbial biomass, TRS, and nutrients from terminal extractions were assessed for incubation temperatures using an anova analysis with interaction effects. TRS showed significant variation with Incubation temperature, pre-incubation temperature, and interaction. Microbial biomass carbon also showed significant variation with pre-incubation temperature, but not incubation temperature. All nutrients had no significant variation. 

```{r , fig.height=6, fig.width=6}
tar_read(Stats_Table)
```
</details>

---

## Session Info 

<details>
  <summary> Session Info </summary>

Date run: `r Sys.Date()`

```{r}
sessionInfo()
```

</details>