---
title: "PCA filtered and detailed"
output: 
  github_document:
  html_preview: true
  always_allow_html: true
  
date: "2023-05-03"
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE
                      )
```

## Volcano

<details>
  <summary>click to open</summary>

#### GC:


```{r , fig.height=5, fig.width=5, results='hide', fig.show="hold", out.width="100%"}

  tar_read(GC_volcano)$GC_Volcano

 
```


#### LC:


```{r , fig.height=5, fig.width=5, results='hide', fig.show="hold", out.width="100%"}
  
  tar_read(LC_volcano)$LC_Volcano
  
  
```



</details>




## PCA vs PLS GC

<details>
  <summary>click to open</summary>

#### Pre:


```{r , fig.height=5, fig.width=5, results='hide', fig.show="hold", out.width="50%"}

  tar_read(gg_GC_PCA)$gg_pca_pre1
  tar_read(gg_GC_PLS)$PLS_pre

 
```


#### INC:


```{r , fig.height=5, fig.width=5, results='hide', fig.show="hold", out.width="50%"}
  
  tar_read(gg_GC_PCA)$gg_pca_inc1
  tar_read(gg_GC_PLS)$PLS_inc
  
  
```



</details>



## PCA vs PLS LC

<details>
  <summary>click to open</summary>

#### Pre:


```{r , fig.height=5, fig.width=5, results='hide', fig.show="hold", out.width="50%"}

  tar_read(gg_LC_PCA)$gg_pca_pre1
  tar_read(gg_LC_PLS)$PLS_pre

 
```


#### INC:


```{r , fig.height=5, fig.width=5, results='hide', fig.show="hold", out.width="50%"}
  
  tar_read(gg_LC_PCA)$gg_pca_inc1
  tar_read(gg_LC_PLS)$PLS_inc
  
  
```



</details>



## PCA vs PLS Lipid

<details>
  <summary>click to open</summary>

#### Pre:


```{r , fig.height=5, fig.width=5, results='hide', fig.show="hold", out.width="50%"}

  tar_read(gg_Lipid)$gg_pca_pre
  tar_read(gg_Lipid_PLS)$PLS_pre

 
```


#### INC:


```{r , fig.height=5, fig.width=5, results='hide', fig.show="hold", out.width="50%"}
  
  tar_read(gg_Lipid)$gg_pca_inc
  tar_read(gg_Lipid_PLS)$PLS_inc
  
  
```



</details>



## PCA vs PLS FTICR

<details>
  <summary>click to open</summary>

#### -2:


```{r , fig.height=5, fig.width=5, results='hide', fig.show="hold", out.width="50%"}

  tar_read(gg_FTICR_PCA_filter_N2N6)$gg_pca_by_pre_polar_N2
  tar_read(gg_FTICR_PLS)$PolarPLS2
  tar_read(gg_FTICR_PCA_filter_N2N6)$gg_pca_by_pre_nonpolar_N2
  tar_read(gg_FTICR_PLS)$nonPolarPLS2
 
```


#### -6:


```{r , fig.height=5, fig.width=5, results='hide', fig.show="hold", out.width="50%"}
  
  tar_read(gg_FTICR_PCA_filter_N2N6)$gg_pca_by_pre_polar_N6
  tar_read(gg_FTICR_PLS)$PolarPLS6
  tar_read(gg_FTICR_PCA_filter_N2N6)$gg_pca_by_pre_nonpolar_N6
  tar_read(gg_FTICR_PLS)$nonPolarPLS6
  
```



</details>


## NOSC by polar and non polar

<details>
  <summary>click to open</summary>

#### NOSC:
```{r , fig.height=5, fig.width=5}
  tar_read(gg_FTICR_NOSC)$gg_nosc
```

```{r , fig.height=5, fig.width=5, results='hide', fig.show="hold", out.width="50%"}
  tar_read(gg_FTICR_NOSC)$gg_nosc_polar
  tar_read(gg_FTICR_NOSC)$gg_nosc_nonpolar
```
</details>

## FTICR PCA Class vs Detailed class

<details>
  <summary>click to open</summary>

#### PCA-Class vs Detailed Class:


```{r , fig.height=5, fig.width=5, results='hide', fig.show="hold", out.width="50%"}
  tar_read(gg_FTICR_PCA)$gg_pca_by_pre_polar
  tar_read(gg_FTICR_PCA_DetailedClass)$gg_pca_by_pre_polar

  tar_read(gg_FTICR_PCA)$gg_pca_by_pre_nonpolar
  tar_read(gg_FTICR_PCA_DetailedClass)$gg_pca_by_pre_nonpolar
  
  tar_read(gg_FTICR_PCA)$gg_pca_by_inc_polar
  tar_read(gg_FTICR_PCA_DetailedClass)$gg_pca_by_inc_polar
  
  tar_read(gg_FTICR_PCA)$gg_pca_by_inc_nonpolar
  tar_read(gg_FTICR_PCA_DetailedClass)$gg_pca_by_inc_nonpolar
  
  
  
  
  
```


</details>





## FTICR PCA seperated pre incubation temps

<details>
  <summary>click to open</summary>

#### PCA -2:


```{r , fig.height=5, fig.width=5, results='hide', fig.show="hold", out.width="50%"}
  tar_read(gg_FTICR_PCA_filter_N2N6)$gg_pca_polar_nonpolar_N2
tar_read(gg_FTICR_PCA_filter_N2N6_2)$gg_pca_polar_nonpolar_N2
   tar_read(gg_FTICR_PCA_filter_N2N6)$gg_pca_polar_nonpolar_pre_N2
   tar_read(gg_FTICR_PCA_filter_N2N6_2)$gg_pca_polar_nonpolar_pre_N2
  tar_read(gg_FTICR_PCA_filter_N2N6)$gg_pca_by_pre_polar_N2
  tar_read(gg_FTICR_PCA_filter_N2N6_2)$gg_pca_by_pre_polar_N2
  tar_read(gg_FTICR_PCA_filter_N2N6)$gg_pca_by_pre_nonpolar_N2
  tar_read(gg_FTICR_PCA_filter_N2N6_2)$gg_pca_by_pre_nonpolar_N2
 
```


#### PCA -6:


```{r , fig.height=5, fig.width=5, results='hide', fig.show="hold", out.width="50%"}
  tar_read(gg_FTICR_PCA_filter_N2N6)$gg_pca_polar_nonpolar_N6
  tar_read(gg_FTICR_PCA_filter_N2N6_2)$gg_pca_polar_nonpolar_N6
  tar_read(gg_FTICR_PCA_filter_N2N6)$gg_pca_polar_nonpolar_pre_N6
  tar_read(gg_FTICR_PCA_filter_N2N6_2)$gg_pca_polar_nonpolar_pre_N6
  tar_read(gg_FTICR_PCA_filter_N2N6)$gg_pca_by_pre_polar_N6
  tar_read(gg_FTICR_PCA_filter_N2N6_2)$gg_pca_by_pre_polar_N6
  tar_read(gg_FTICR_PCA_filter_N2N6)$gg_pca_by_pre_nonpolar_N6
  tar_read(gg_FTICR_PCA_filter_N2N6_2)$gg_pca_by_pre_nonpolar_N6
  
```



</details>


## FTICR PCA seperated incubation temp
### DO NOT OPEN

<details>
  <summary>click to open</summary>

#### PCA-Pre:


```{r , fig.height=5, fig.width=5, results='hide', fig.show="hold", out.width="50%"}
  tar_read(gg_FTICR_PCA_filter)$gg_pca_polar_nonpolar_Pre
tar_read(gg_FTICR_PCA_filter_DetailedClass)$gg_pca_polar_nonpolar_Pre
   tar_read(gg_FTICR_PCA_filter)$gg_pca_polar_nonpolar_pre_Pre
   tar_read(gg_FTICR_PCA_filter_DetailedClass)$gg_pca_polar_nonpolar_pre_Pre
  tar_read(gg_FTICR_PCA_filter)$gg_pca_by_pre_polar_Pre
  tar_read(gg_FTICR_PCA_filter_DetailedClass)$gg_pca_by_pre_polar_Pre
  tar_read(gg_FTICR_PCA_filter)$gg_pca_by_pre_nonpolar_Pre
  tar_read(gg_FTICR_PCA_filter_DetailedClass)$gg_pca_by_pre_nonpolar_Pre
 
```


#### PCA-2:


```{r , fig.height=5, fig.width=5, results='hide', fig.show="hold", out.width="50%"}
  tar_read(gg_FTICR_PCA_filter)$gg_pca_polar_nonpolar_2
  tar_read(gg_FTICR_PCA_filter_DetailedClass)$gg_pca_polar_nonpolar_2
  tar_read(gg_FTICR_PCA_filter)$gg_pca_polar_nonpolar_pre_2
  tar_read(gg_FTICR_PCA_filter_DetailedClass)$gg_pca_polar_nonpolar_pre_2
  tar_read(gg_FTICR_PCA_filter)$gg_pca_by_pre_polar_2
  tar_read(gg_FTICR_PCA_filter_DetailedClass)$gg_pca_by_pre_polar_2
  tar_read(gg_FTICR_PCA_filter)$gg_pca_by_pre_nonpolar_2
  tar_read(gg_FTICR_PCA_filter_DetailedClass)$gg_pca_by_pre_nonpolar_2
  
```

#### PCA-4:


```{r , fig.height=5, fig.width=5, results='hide', fig.show="hold", out.width="50%"}
  tar_read(gg_FTICR_PCA_filter)$gg_pca_polar_nonpolar_4
  tar_read(gg_FTICR_PCA_filter_DetailedClass)$gg_pca_polar_nonpolar_4
  tar_read(gg_FTICR_PCA_filter)$gg_pca_polar_nonpolar_pre_4
  tar_read(gg_FTICR_PCA_filter_DetailedClass)$gg_pca_polar_nonpolar_pre_4
  tar_read(gg_FTICR_PCA_filter)$gg_pca_by_pre_polar_4
  tar_read(gg_FTICR_PCA_filter_DetailedClass)$gg_pca_by_pre_polar_4
  tar_read(gg_FTICR_PCA_filter)$gg_pca_by_pre_nonpolar_4
  tar_read(gg_FTICR_PCA_filter_DetailedClass)$gg_pca_by_pre_nonpolar_4
  
```

#### PCA-6:


```{r , fig.height=5, fig.width=5, results='hide', fig.show="hold", out.width="50%"}
  tar_read(gg_FTICR_PCA_filter)$gg_pca_polar_nonpolar_6
  tar_read(gg_FTICR_PCA_filter_DetailedClass)$gg_pca_polar_nonpolar_6
  tar_read(gg_FTICR_PCA_filter)$gg_pca_polar_nonpolar_pre_6
  tar_read(gg_FTICR_PCA_filter_DetailedClass)$gg_pca_polar_nonpolar_pre_6
  tar_read(gg_FTICR_PCA_filter)$gg_pca_by_pre_polar_6
   tar_read(gg_FTICR_PCA_filter_DetailedClass)$gg_pca_by_pre_polar_6
  tar_read(gg_FTICR_PCA_filter)$gg_pca_by_pre_nonpolar_6
  tar_read(gg_FTICR_PCA_filter_DetailedClass)$gg_pca_by_pre_nonpolar_6
  
```

#### PCA-8:


```{r , fig.height=5, fig.width=5, results='hide', fig.show="hold", out.width="50%"}
  tar_read(gg_FTICR_PCA_filter)$gg_pca_polar_nonpolar_8
  tar_read(gg_FTICR_PCA_filter_DetailedClass)$gg_pca_polar_nonpolar_8
  tar_read(gg_FTICR_PCA_filter)$gg_pca_polar_nonpolar_pre_8
  tar_read(gg_FTICR_PCA_filter_DetailedClass)$gg_pca_polar_nonpolar_pre_8
  tar_read(gg_FTICR_PCA_filter)$gg_pca_by_pre_polar_8
  tar_read(gg_FTICR_PCA_filter_DetailedClass)$gg_pca_by_pre_polar_8
  tar_read(gg_FTICR_PCA_filter)$gg_pca_by_pre_nonpolar_8
   tar_read(gg_FTICR_PCA_filter_DetailedClass)$gg_pca_by_pre_nonpolar_8
  
```


#### PCA-10:


```{r , fig.height=5, fig.width=5, results='hide', fig.show="hold", out.width="50%"}
  tar_read(gg_FTICR_PCA_filter)$gg_pca_polar_nonpolar_10
  tar_read(gg_FTICR_PCA_filter_DetailedClass)$gg_pca_polar_nonpolar_10
  
  tar_read(gg_FTICR_PCA_filter)$gg_pca_polar_nonpolar_pre_10
  tar_read(gg_FTICR_PCA_filter_DetailedClass)$gg_pca_polar_nonpolar_pre_10
  
  tar_read(gg_FTICR_PCA_filter)$gg_pca_by_pre_polar_10
  tar_read(gg_FTICR_PCA_filter_DetailedClass)$gg_pca_by_pre_polar_10
  
  tar_read(gg_FTICR_PCA_filter)$gg_pca_by_pre_nonpolar_10
  tar_read(gg_FTICR_PCA_filter_DetailedClass)$gg_pca_by_pre_nonpolar_10
```





</details>

---

## Session Info 

<details>
  <summary> Session Info </summary>

Date run: `r Sys.Date()`

```{r}
sessionInfo()
```

</details>