---
title: "SCGSR final report"
output: pdf_document
          
date: "2023-06-21"
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE
                      )
```

## Sample Summary


Soils from northwest Alaska were homogenized and pre-incubated at -2 and -6 degrees Celsius for three months after which they were incubated at 2,4,6,8,10 degrees Celsius for one week. After the week long incubation soils were extracted using 0.5M K2SO4, and chloroform extracted to measure microbial biomass and nutrient concentrations. Sub-samples were also sent to PNNL for MPLEx (Methanol chloroform extraction) to provide more comprehensive analysis of the molecular composition of organic matter using FT-ICR, NMR, GC-MS and LC-MS techniques. Lipidomics were also performed to ascertain if there were any significant shifts in microbial biomass.



---

## Respiration Results


Respiration measurements were taken daily during the incubation using a Li-850 bench top respiration unit. Below are the respiration rates for each sample, as well as the calculates total C respired.  Linear mixed effects model showed significant respiration variation by incubation and pre incubation temperatures. An asterisks indicates a significant (p<= 0.05, ANOVA) difference in pre-incubation temperature. 

```{r , fig.height=6, fig.width=9}
tar_read(gg_respiration)$gg_N_Legend
```




---

## Soil Nutrients

Soil K2SO4 extracts were utilized to measure ammonium, Nitrate, Total free primary amines, phosphate, Total reducing sugars. Below are the concentration data. An asterisks indicates a significant (p<= 0.05, ANOVA) difference in pre-incubation temperature. 

```{r , fig.height=6, fig.width=6}
tar_read(gg_nutrients)$`Total reducing sugars`
```
```{r , fig.height=12, fig.width=12}
tar_read(gg_nutrients)$`Nutrient combined`
```



---

## Microbial Biomass


Soil K2SO4 extracts were utilized to measure ammonium, Nitrate, Total free primary amines, phosphate, Total reducing sugars. Below is the concentration data.An asterisks indicates a significant (p<= 0.05,ANOVA) difference in pre-incubation temperature.

```{r , fig.height=6, fig.width=9}
tar_read(gg_MicrobialBiomass)$"Total Biomass"
```



---

## GC-MS


  
  Below is the relative quantification of compounds identified by gas chromatography within the MPLEx extracts.Little to no variation was identified that corresponds to the more broad metrics above in the soil nutrient section. The majority of compounds measured were unidentified.  Volcano plot can be used to identify the compounds that are significantly greater between pre incubation temperature (p<0.05, ANOVA). After which we used a PCA to visualize separation between the pre incubation temperatures across significantly different compounds. PERMANOVA results are displayed in the table below the PCAs to show variation between treatments. 
  

```{r , fig.height=5, fig.width=5, results='hide', fig.show="hold", out.width="100%"}

  tar_read(GC_volcano)$GC_Volcano
 
```

```{r , fig.height=5, fig.width=5, results='hide', fig.show="hold", out.width="50%"}
tar_read(gg_GC_PCA)$gg_pca_pre_Sig
  tar_read(gg_GC_PCA)$gg_pca_inc_Sig
```

```{r , fig.height=5, fig.width=5, out.width="100%"}
  tar_read(gg_GC_PCA)$permanova_GC_sig
 
```




---

## LC-MS


  
   Below is the relative quantification of compounds identified by liquid chromatography within the MPLEx extracts.Little to no variation was identified that corresponds to the more broad metrics above in the soil nutrient section. The majority of compounds measured were unidentified.  Volcano plot can be used to identify the compounds that are significantly greater between pre incubation temperature (p<0.05, ANOVA). After which we used a PCA to visualize separation between the pre incubation temperatures across significantly different compounds. PERMANOVA results are displayed in the table below the PCAs to show variation between treatments. 
   
```{r , fig.height=5, fig.width=5, results='hide', fig.show="hold", out.width="100%"}
  
  tar_read(LC_volcano)$LC_Volcano
  
  
```
   
   
```{r , fig.height=5, fig.width=5, results='hide', fig.show="hold", out.width="50%"}
  tar_read(gg_LC_PCA)$gg_pca_pre_Sig
  tar_read(gg_LC_PCA)$gg_pca_inc_Sig
  
  
```
```{r , fig.height=5, fig.width=5, out.width="100%"}
  tar_read(gg_LC_PCA)$permanova_LC_sig
 
```




---

## Lipids

  
 Lipid analysis was done via liquid chrometography on MEPLEx extracts. Some variation was identified between pre-incubation temperatures, though little was biologically significant. Conclusion that small changes in biomass were present but not significant. A big missing piece to this analysis would be community composition.Little no no variation was observed within this data set. PCAs below show little to no separation between incubation and pre incubation temperatures. 
 

```{r , fig.height=5, fig.width=5, results='hide', fig.show="hold", out.width="50%"}

tar_read(gg_Lipid)$gg_pca_pre
tar_read(gg_Lipid)$gg_pca_inc

```
```{r , fig.height=5, fig.width=5, fig.show="hold", out.width="100%"}

tar_read(gg_Lipid)$permanova_Lipid_all

```
```{r , fig.height=5, fig.width=5, results='hide', fig.show="hold", out.width="50%"}

tar_read(gg_Lipid)$gg_pca_pre_pos
tar_read(gg_Lipid)$gg_pca_inc_pos

```
```{r , fig.height=5, fig.width=5, fig.show="hold", out.width="100%"}

tar_read(gg_Lipid)$permanova_Lipid_all2

```
```{r , fig.height=5, fig.width=5, results='hide', fig.show="hold", out.width="50%"}


tar_read(gg_Lipid)$gg_pca_pre_neg
tar_read(gg_Lipid)$gg_pca_inc_neg

```
```{r , fig.height=5, fig.width=5, fig.show="hold", out.width="100%"}
tar_read(gg_Lipid)$permanova_Lipid_all3

```




---

## FT-MS (FT-ICR)



FTICR was performed on MEPLEx extracts to gain a qualitative understanding of the changes in organic matter composition after the incubation. There appear to be differences between pre-incubation temperatures, particularly in terms of the number of unique compounds, which could be indicative of microbial processing of organic matter and production of new organic compounds. 

### FTICR  Van krevelen diagrams:

  
```{r , fig.height=9, fig.width=9}
ggExtra::ggMarginal(gg_FTICR_vk$gg_vk_polar_nonpolar, groupColour = TRUE, groupFill = TRUE, alpha = 0.1)

```

```{r , fig.height=9, fig.width=9}
tar_read(gg_FTICR_vk)$gg_vk_domains

```


### FTICR  Common vs unique peaks by treatment:



#### All


```{r , fig.height=6, fig.width=6}
NULL
tar_read(gg_FTICR_unique)$gg_common_unique_sep_inc_pre
tar_read(gg_FTICR_unique)$gg_common_unique_sep_inc_pre_seperated
tar_read(gg_FTICR_unique)$fticr_unique_summary_sep_inc_pre
  
```




#### Polar



```{r , fig.height=6, fig.width=6}
NULL
tar_read(gg_FTICR_unique_polar)$gg_common_unique_sep_inc_pre
tar_read(gg_FTICR_unique_polar)$gg_common_unique_sep_inc_pre_seperated
tar_read(gg_FTICR_unique_polar)$fticr_unique_summary_sep_inc_pre
  


```



#### Non-Polar



```{r , fig.height=6, fig.width=6}

NULL
tar_read(gg_FTICR_unique_nonpolar)$gg_common_unique_sep_inc_pre
tar_read(gg_FTICR_unique_nonpolar)$ gg_common_unique_sep_inc_pre_seperated 
tar_read(gg_FTICR_unique_nonpolar)$fticr_unique_summary_sep_inc_pre



```



### FTICR  relative abundance and PCAs:

  
#### Relative Abundance


```{r , fig.height=6, fig.width=9}

tar_read(gg_FTICR_relabund)$relabund

tar_read(gg_FTICR_relabund)$relabund_p

tar_read(gg_FTICR_relabund)$relabund_np
```

```{r , fig.height=5, fig.width=5, results='hide', fig.show="hold", out.width="50%"}
```

```{r , fig.height=5, fig.width=5, results='hide', fig.show="hold", out.width="50%"}
NULL
  tar_read(gg_FTICR_PCA)$gg_pca_by_pre_polar
   tar_read(gg_FTICR_PCA)$gg_pca_by_inc_polar
```

```{r , fig.height=5, fig.width=5,fig.show="hold",out.width="100%"}
tar_read(gg_FTICR_permanova)$permanova_fticr_polar
```

```{r , fig.height=5, fig.width=5, results='hide', fig.show="hold", out.width="50%"}
  tar_read(gg_FTICR_PCA)$gg_pca_by_pre_nonpolar
  tar_read(gg_FTICR_PCA)$gg_pca_by_inc_nonpolar
  
```

```{r , fig.height=5, fig.width=5,fig.show="hold",out.width="100%"}
 tar_read(gg_FTICR_permanova)$permanova_fticr_nonpolar
```



---

## Session Info 



Date run: `r Sys.Date()`

```{r}
sessionInfo()
```
