---
title: "SCGSR final report"
output: html_document
date: "2023-05-03"
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE
                      )
```

## Sample Summary

<details>
  <summary>click to open</summary>
Soils from northwest Alaska were homogenized and pre-incubated at -2 and -6 degrees Celsius for three months after which they were incubated at 2,4,6,8,10 degrees Celsius for one week. After the week long incubation soils were extracted using 0.5M K2SO4, and chloroform extracted to measure microbial biomass and nutrient concentrations. Sub-samples were also sent to PNNL for more comprehensive analysis of organic matter using FTICR, NMR, GC-MS and LC-MS techniques. Lipidomics were also performed to ascertain if there were any significant shifts lipids.

```{r analyte-completion, eval= TRUE}
tar_read(sample_key) %>% knitr::kable()
```

</details>

---

## Respiration Results

<details>
  <summary>click to open</summary>
Respiration measurements were taken daily during the incubation using a Li-850 bench top respiration unit. Below are the respiration rates for each sample, as well as the calculates total C respired.  

```{r , fig.height=6, fig.width=9}
tar_read(gg_respiration)$gg_N_Legend
tar_read(Stats_Table)$"Respiration statistics: anova(lme(Res ~ JD2 + Inc_temp + pre_inc,random = ~1|Sample_ID))"
tar_read(Stats_Table)$LastRES_aov
```

</details>


---

## Soil Nutrients
<details>
  <summary>click to open</summary>
Soil K2SO4 extracts were utilized to measure ammonium, Nitrate, Total free primary amines, phosphate, Total reducing sugars. Below are the concentration data. An asterisks indicates a significant (p<= 0.05) difference in pre-incubation temperature. 

```{r , fig.height=6, fig.width=6}
tar_read(gg_nutrients)$`Total reducing sugars`
tar_read(gg_nutrients)$`Nutrient combined`
tar_read(Stats_Table)$all_aov3
```

</details>

---

## Microbial Biomass

<details>
  <summary>click to open</summary>
Soil K2SO4 extracts were utilized to measure ammonium, Nitrate, Total free primary amines, phosphate, Total reducing sugars. Below is the concentration data.An asterisks indicates a significant (p<= 0.05) difference in pre-incubation temperature.

```{r , fig.height=3, fig.width=6}
tar_read(gg_MicrobialBiomass)$"Total Biomass"
tar_read(Stats_Table)$all_aov4
```

</details>

---

## GC

<details>
  <summary>click to open</summary>


```{r , fig.height=15, fig.width=20}
tar_read(gg_GC)$GC
tar_read(gg_GC)$StatsGC
```

</details>

---

## LC

<details>
  <summary>click to open</summary>
 

```{r , fig.height=15, fig.width=20}
tar_read(gg_LC)$LC_pos
tar_read(gg_LC)$LC_neg
tar_read(gg_LC)$StatsLC
```

</details>


---

## Lipids

<details>
  <summary>click to open</summary>
 

```{r , fig.height=6, fig.width=9}

tar_read(gg_Lipid)$Lipid_pos2
tar_read(gg_Lipid)$Lipid_neg2
tar_read(gg_Lipid)$permanova_Lipid_all

```

</details>

---

## FTICR

<details>
  <summary>click to open</summary>

### FTICR  Van krevalin diagrams:

<details>
  <summary>click to open</summary>
  
```{r , fig.height=9, fig.width=9}
ggExtra::ggMarginal(gg_FTICR$gg_vk_polar_nonpolar, groupColour = TRUE, groupFill = TRUE, alpha = 0.1)

```

```{r , fig.height=9, fig.width=9}
tar_read(gg_FTICR)$gg_vk_domains
tar_read(gg_FTICR)$gg_vk_all
tar_read(gg_FTICR)$gg_vk_all_pre
```
</details>

### FTICR  Common vs unique peaks by treatment:

<details>
  <summary>click to open</summary>

```{r , fig.height=6, fig.width=6}
tar_read(gg_FTICR)$gg_unique_pre
tar_read(gg_FTICR)$gg_common_unique
tar_read(gg_FTICR)$fticr_unique_summary
  tar_read(gg_FTICR)$gg_common_unique_inc
  tar_read(gg_FTICR)$fticr_unique_summary_inc
  tar_read(gg_FTICR)$gg_common_unique_inc_pre
  tar_read(gg_FTICR)$fticr_unique_summary_inc_pre
  
```
</details>

### FTICR  Permanova results and PCAs:

<details>
  <summary>click to open</summary>

```{r , fig.height=6, fig.width=6}
tar_read(gg_FTICR)$relabund
tar_read(gg_FTICR)$permanova_fticr_all

```
#### PCA results:
```{r , fig.height=6, fig.width=6}
tar_read(gg_FTICR)$gg_pca_polar_nonpolar

  tar_read(gg_FTICR)$gg_pca_by_pre_polar
  tar_read(gg_FTICR)$gg_pca_by_pre_nonpolar
  
  tar_read(gg_FTICR)$gg_pca_by_inc_polar
  tar_read(gg_FTICR)$gg_pca_by_inc_nonpolar
```
</details>




</details>

---

## Session Info 

<details>
  <summary> Session Info </summary>

Date run: `r Sys.Date()`

```{r}
sessionInfo()
```

</details>