---
title: "SCGSR final report"
output: 
  github_document:
  html_preview: true
  always_allow_html: true
  
date: "2023-05-03"
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE
                      )
```

## Sample Summary

<details>
  <summary>click to open</summary>
Soils from northwest Alaska were homogenized and pre-incubated at -2 and -6 degrees Celsius for three months after which they were incubated at 2,4,6,8,10 degrees Celsius for one week. After the week long incubation soils were extracted using 0.5M K2SO4, and chloroform extracted to measure microbial biomass and nutrient concentrations. Sub-samples were also sent to PNNL for MPLEx (Methanol chloroform extraction) to provide more comprehensive analysis of the molecular composition of organic matter using FT-ICR, NMR, GC-MS and LC-MS techniques. Lipidomics were also performed to ascertain if there were any significant shifts in microbial biomass.

```{r analyte-completion, eval= TRUE}
tar_read(sample_key) %>% knitr::kable()
```

</details>

---

## Respiration Results

<details>
  <summary>click to open</summary>
Respiration measurements were taken daily during the incubation using a Li-850 bench top respiration unit. Below are the respiration rates for each sample, as well as the calculates total C respired.  

```{r , fig.height=6, fig.width=9}
tar_read(gg_respiration)$gg_N_Legend
tar_read(Stats_Table)$"Respiration statistics: anova(lme(Res ~ JD2 + Inc_temp + pre_inc,random = ~1|Sample_ID))"
tar_read(Stats_Table)$LastRES_aov
```

</details>


---

## Soil Nutrients
<details>
  <summary>click to open</summary>
Soil K2SO4 extracts were utilized to measure ammonium, Nitrate, Total free primary amines, phosphate, Total reducing sugars. Below are the concentration data. An asterisks indicates a significant (p<= 0.05) difference in pre-incubation temperature. 

```{r , fig.height=6, fig.width=6}
tar_read(gg_nutrients)$`Total reducing sugars`
```
```{r , fig.height=12, fig.width=12}
tar_read(gg_nutrients)$`Nutrient combined`
tar_read(Stats_Table)$all_aov3
```

</details>

---

## Microbial Biomass

<details>
  <summary>click to open</summary>
Soil K2SO4 extracts were utilized to measure ammonium, Nitrate, Total free primary amines, phosphate, Total reducing sugars. Below is the concentration data.An asterisks indicates a significant (p<= 0.05) difference in pre-incubation temperature.

```{r , fig.height=6, fig.width=9}
tar_read(gg_MicrobialBiomass)$"Total Biomass"
tar_read(Stats_Table)$all_aov4
```

</details>

---

## GC-MS

<details>
  <summary>click to open</summary>
  
<details>
  <summary>click to open</summary>

```{r , fig.height=15, fig.width=20}
tar_read(gg_GC)$GC
tar_read(gg_GC)$GC_sac
```

<details>
  <summary>click to open ANOVA table</summary>
```{r , fig.height=15, fig.width=20}
tar_read(gg_GC)$StatsGC
```
</details>
</details>

#### PCA
<details>
  <summary>click to open</summary>


```{r , fig.height=6, fig.width=9}
NULL
tar_read(gg_GC_PCA)$gg_pca_pre1
tar_read(gg_GC_PCA)$gg_pca_inc1
tar_read(gg_GC_PCA)$permanova_GC_all
NULL
tar_read(gg_GC_PCA)$gg_pca_pre2
tar_read(gg_GC_PCA)$gg_pca_inc2
tar_read(gg_GC_PCA)$permanova_GC_all2
```

</details>



</details>

---

## LC-MS

<details>
  <summary>click to open</summary>
 
 <details>
  <summary>click to open</summary>

```{r , fig.height=15, fig.width=20}
tar_read(gg_LC)$LC_pos
tar_read(gg_LC)$LC_neg
tar_read(gg_LC)$LC_pos_sac
tar_read(gg_LC)$LC_neg_sac
```


<details>
  <summary>click to open ANOVA table</summary>

```{r , fig.height=15, fig.width=20}
tar_read(gg_LC)$StatsLC
```
</details>
</details>
#### PCA
<details>
  <summary>click to open</summary>


```{r , fig.height=6, fig.width=9}
NULL
tar_read(gg_LC_PCA)$gg_pca_pre1
tar_read(gg_LC_PCA)$gg_pca_inc1
tar_read(gg_LC_PCA)$permanova_LC_all
NULL
tar_read(gg_LC_PCA)$gg_pca_pre2
tar_read(gg_LC_PCA)$gg_pca_inc2
tar_read(gg_LC_PCA)$permanova_LC_all2
```

</details>



</details>


---

## Lipids

<details>
  <summary>click to open</summary>
 
<details>
  <summary>click to open</summary>
```{r , fig.height=6, fig.width=9}

tar_read(gg_Lipid)$Lipid_pos2
tar_read(gg_Lipid)$Lipid_neg2

```

<details>
  <summary>click to open ANOVA table</summary>
```{r , fig.height=6, fig.width=9}
tar_read(gg_Lipid)$StatsLipid
```
</details>

</details>

<details>
  <summary>click to open</summary>
```{r , fig.height=6, fig.width=9}
NULL
tar_read(gg_Lipid)$gg_pca_pre
tar_read(gg_Lipid)$gg_pca_inc
tar_read(gg_Lipid)$permanova_Lipid_all
NULL
tar_read(gg_Lipid)$gg_pca_pre_pos
tar_read(gg_Lipid)$gg_pca_inc_pos
tar_read(gg_Lipid)$permanova_Lipid_all2
NULL
tar_read(gg_Lipid)$gg_pca_pre_neg
tar_read(gg_Lipid)$gg_pca_inc_neg
tar_read(gg_Lipid)$permanova_Lipid_all3

```
</details>



</details>
---

## FT-MS (FT-ICR)

<details>
  <summary>click to open</summary>

### FTICR  Van krevelen diagrams:

<details>
  <summary>click to open</summary>
  
```{r , fig.height=9, fig.width=9}
ggExtra::ggMarginal(gg_FTICR_vk$gg_vk_polar_nonpolar, groupColour = TRUE, groupFill = TRUE, alpha = 0.1)

```

```{r , fig.height=9, fig.width=9}
tar_read(gg_FTICR_vk)$gg_vk_domains
tar_read(gg_FTICR_vk)$gg_vk_all
tar_read(gg_FTICR_vk)$gg_vk_all_pre
```
</details>

### FTICR  Common vs unique peaks by treatment:

<details>
  <summary>click to open</summary>

#### All

<details>
  <summary>click to open</summary>

```{r , fig.height=6, fig.width=6}
NULL
tar_read(gg_FTICR_unique)$gg_unique_pre
tar_read(gg_FTICR_unique)$gg_common_unique
tar_read(gg_FTICR_unique)$fticr_unique_summary
NULL
tar_read(gg_FTICR_unique)$gg_common_unique_inc
tar_read(gg_FTICR_unique)$fticr_unique_summary_inc
NULL
tar_read(gg_FTICR_unique)$gg_common_unique_inc_pre
tar_read(gg_FTICR_unique)$fticr_unique_summary_inc_pre
NULL
tar_read(gg_FTICR_unique)$gg_common_unique_sep_inc_pre
tar_read(gg_FTICR_unique)$gg_common_unique_sep_inc_pre_seperated
tar_read(gg_FTICR_unique)$fticr_unique_summary_sep_inc_pre
  
```

</details>



#### Polar

<details>
  <summary>click to open</summary>

```{r , fig.height=6, fig.width=6}
NULL
tar_read(gg_FTICR_unique_polar)$gg_unique_pre
tar_read(gg_FTICR_unique_polar)$gg_common_unique
tar_read(gg_FTICR_unique_polar)$fticr_unique_summary
NULL
tar_read(gg_FTICR_unique_polar)$gg_common_unique_inc
tar_read(gg_FTICR_unique_polar)$fticr_unique_summary_inc
NULL
tar_read(gg_FTICR_unique_polar)$gg_common_unique_inc_pre
tar_read(gg_FTICR_unique_polar)$fticr_unique_summary_inc_pre
NULL
tar_read(gg_FTICR_unique_polar)$gg_common_unique_sep_inc_pre
tar_read(gg_FTICR_unique_polar)$gg_common_unique_sep_inc_pre_seperated
tar_read(gg_FTICR_unique_polar)$fticr_unique_summary_sep_inc_pre
  


```

</details>

#### Non-Polar

<details>
  <summary>click to open</summary>

```{r , fig.height=6, fig.width=6}
NULL
tar_read(gg_FTICR_unique_nonpolar)$gg_unique_pre
tar_read(gg_FTICR_unique_nonpolar)$gg_common_unique
tar_read(gg_FTICR_unique_nonpolar)$fticr_unique_summary
NULL
tar_read(gg_FTICR_unique_nonpolar)$gg_common_unique_inc
tar_read(gg_FTICR_unique_nonpolar)$fticr_unique_summary_inc
NULL
tar_read(gg_FTICR_unique_nonpolar)$gg_common_unique_inc_pre
tar_read(gg_FTICR_unique_nonpolar)$fticr_unique_summary_inc_pre
NULL
tar_read(gg_FTICR_unique_nonpolar)$gg_common_unique_sep_inc_pre
tar_read(gg_FTICR_unique_nonpolar)$ gg_common_unique_sep_inc_pre_seperated 
tar_read(gg_FTICR_unique_nonpolar)$fticr_unique_summary_sep_inc_pre



```


</details>

</details>

### FTICR  Permanova results and PCAs:

<details>
  <summary>click to open</summary>
  
#### Relative Abundance

<details>
  <summary>click to open</summary>

```{r , fig.height=6, fig.width=9}
NULL
tar_read(gg_FTICR_relabund)$relabund
tar_read(FTICR_relabund)$Total_Relabund_aov
NULL
tar_read(gg_FTICR_relabund)$relabund_p
tar_read(FTICR_relabund)$Polar_Relabund_aov
NULL
tar_read(gg_FTICR_relabund)$relabund_np
tar_read(FTICR_relabund)$NonPolar_Relabund_aov
```

</details>

#### PCA results:

<details>
  <summary>click to open</summary>


```{r , fig.height=6, fig.width=6}
NULL
tar_read(gg_FTICR_PCA)$gg_pca_polar_nonpolar
tar_read(gg_FTICR_PCA)$gg_pca_polar_nonpolar_pre
tar_read(gg_FTICR_PCA)$gg_pca_polar_nonpolar_inc
tar_read(gg_FTICR_permanova)$permanova_fticr_all_with_polar
tar_read(gg_FTICR_permanova)$permanova_fticr_all
NULL

  tar_read(gg_FTICR_PCA)$gg_pca_by_pre_polar
   tar_read(gg_FTICR_PCA)$gg_pca_by_inc_polar
   tar_read(gg_FTICR_permanova)$permanova_fticr_polar
   NULL
   
  tar_read(gg_FTICR_PCA)$gg_pca_by_pre_nonpolar
  tar_read(gg_FTICR_PCA)$gg_pca_by_inc_nonpolar
  tar_read(gg_FTICR_permanova)$permanova_fticr_nonpolar
  NULL
  
  
  tar_read(gg_FTICR_PCA)$gg_pca_polarVnonpolar_pre
  tar_read(gg_FTICR_PCA)$gg_pca_polarVnonpolar_inc
  tar_read(gg_FTICR_permanova)$permanova_fticr_PolarSeperations
  
```


</details>

</details>

</details>

---

## Session Info 

<details>
  <summary> Session Info </summary>

Date run: `r Sys.Date()`

```{r}
sessionInfo()
```

</details>